Probing the Deuteron at Very Large Internal Momenta

### 2020-10-15 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised_v4.tex
updated prl

\begin{abstract}
  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  over a range of neutron recoil momenta, $p_{\mathrm{r}}$,  reaching up to $\sim1.0$ GeV/c. The data were
  obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
  transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar currents (IC) are suppressed and
  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
  theoretical calculations, where we observe a significant discrepancy for missing momenta $p_{\mathrm{r}}>700$ MeV/c. 
\end{abstract}

@@

carried out at Jefferson Lab (JLab) and Brookhaven National Lab (BNL). In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions

@@

(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions. Due to FSI effects, the measurement of certain missing momentum does not yet guarantee that the initial

@@

\indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.

@@

experiments determined that the cross sections for fixed missing momenta indeed exhibited a strong angular dependence with $\theta_{nq}$, peaking

@@

\indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c. At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to
the lower and higher missing momentum settings, respectively. At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c, which is more than twice the highest neutron recoil momentum

@@

simulation program, SIMC \cite{PhysRevC.64.054610}\cite{cyero_phdthesis}. Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

target boiling inefficiency ($4.2 \%$). The values in parentheses were averaged over all missing momentum settings. \\

@@

determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 

@@

($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the

@@

The calculations use different FF parametrizations which can lead to a 6$\%$ change of the theortical cross section.\\

@@

At the higher missing momenta provided by this experiment ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing

>>>>

\begin{abstract}
  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  over a range of neutron recoil momenta, $p_{\mathrm{r}}$,  reaching up to $\sim1.0$ GeV/c. The data were
  obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
  transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar currents (IC) are suppressed and
  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
  theoretical calculations, where we observe a significant discrepancy for recoil momenta $p_{\mathrm{r}}>700$ MeV/c. 
\end{abstract}

@@

carried out at Jefferson Lab (JLab) \cite{PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501} and Brookhaven National Lab (BNL) \cite{PhysRevLett.97.162504}. In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions

@@

(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions. Due to FSI effects, the measurement of a certain missing momentum does not yet guarantee that the initial

@@

\indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$ (relative angles between recoil momenta $\vec{p}_{\mathrm{r}}$ and 3-momentum transfers $\vec{q}$).

@@

experiments determined that the cross sections for fixed recoil momenta indeed exhibited a strong angular dependence with $\theta_{nq}$, peaking

@@

\indent We measured three central recoil momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c. At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to
the lower and higher recoil momentum settings, respectively. At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c, which is more than twice the highest neutron recoil momentum

@@

simulation program, SIMC \cite{PhysRevC.64.054610}. Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

target boiling inefficiency ($4.2 \%$). The values in parentheses were averaged over all recoil momentum settings. \\

@@

determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each recoil momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 

@@

($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ %\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
is a recoil factor \cite{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the

@@

The calculations use different FF parametrizations which can lead to a $\sim$5.8 -6.6$\%$ variation of the theortical cross section.\\

@@

At the higher recoil momenta provided by this experiment ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data,
potentially illustrating the limit to which a non-relativistic wave function from the solution to the Schr\"{o}dinger equation is valid and able to describe
experimental data that probe the high momentum region of the $np$ system in the most direct way possible.
Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high recoil

### 2020-10-15 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
updated prl

($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the

>>>>

($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ %\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
is a recoil factor \ref{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the
